The problem and promise of scale in multilayer networks

### 2020-01-24 paper/manuscript.Rmd
monolayr

Unlike traditional social networks, multilayer networks explicitly consider social systems across contexts, including scale-dependent contexts (Pilosof et al. 2017). Multilayer networks are made up of multiple layers, each representing different classes of individuals (e.g. male or female), types of behaviours (e.g. grooming, travelling, or foraging), spatial areas (e.g. local or regional), or temporal windows (e.g. daily or seasonal) (Kivela et al. 2014; Porter 2018). Multilayer networks are relatively novel to studies of animal behaviour (Finn et al. 2019; Silk et al. 2018), although they have been used to describe multidimensional human social systems, complex transportation networks, and organismal neural networks (Silk et al. 2018). The role of scale within multilayer social networks remains unexplored but provides a unique opportunity to develop novel understanding of variation in the temporal or spatial scales associated with social systems.

>>>>

Unlike traditional *monolayer* social networks, multilayer networks explicitly consider social systems across contexts, including scale-dependent contexts (Pilosof et al. 2017). Multilayer networks are made up of multiple layers, each representing different classes of individuals (e.g. male or female), types of behaviours (e.g. grooming, travelling, or foraging), spatial areas (e.g. local or regional), or temporal windows (e.g. daily or seasonal) (Kivela et al. 2014; Porter 2018). Multilayer networks are relatively novel to studies of animal behaviour (Finn et al. 2019; Silk et al. 2018), although they have been used to describe multidimensional human social systems, complex transportation networks, and organismal neural networks (Silk et al. 2018). The role of scale within multilayer social networks remains unexplored but provides a unique opportunity to develop novel understanding of variation in the temporal or spatial scales associated with social systems.
